\section{Introduction}
In the field of fashion e-commerce, clothing image data analysis has many valuable applications on specific demand. One common problem for consumers is that they cannot find the exact items even though they already have the images of them, which often come from social media., sometime is hard to find where to buy the similar items, not to mention other items that often go together with. Hence, acknowledge the consumer’s needs from their favorite picture is an advantage to provide effective shopping recommendations, which increase interaction on the trade items and give benefits for both consumers and providers. 
Based on those practical needs, we will separate research question into two main tasks. First, we attend to concentrate on obtaining the method to apply deep learning model on outfit object detection and classification with given clothing images dataset. Then, assuming that the outfit combination from images of dataset are common, we will build a learning model to cluster the combination between items based on different perspectives to provide valuable mix and match recommendations.
The project will have two contributions: (1) Develop a deep learning model for clothing object detection and clothing classification. (2) Develop a recommendation model for clothes mix and match.aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa

\begin{flushleft}
``LaTeX is a document preparation system and document markup 
language. LaTeX uses the TeX typesetting program for formatting 
its output, and is itself written in the TeX macro language. 
LaTeX is not the name of a particular editing program, but refers 
to the encoding or tagging conventions that are used in LaTeX documents".
\end{flushleft}